### 2022-12-02 definitions.tex
details
up

@@

@@

\begin{theorem}
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc bounded resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}

\begin{proof}
pas de effective basis of $post^*$.
\end{proof}

\begin{theorem}
{\sc resilience} is undecidable for WSTS (with upward compatibility) ???
\end{theorem}

>>>>

A \emph{downward-WSTS} is ... \\

@@

applications: PN, les automates a pile sont WSTS avec $post^*$ calculable donc resilience calculable. Mais pas ResetPN.

@@

\begin{theorem}(à prouver)
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

@@

\begin{proposition}(à prouver)
{\sc $k$-resilience}, hence {\sc bounded resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}

\begin{proof}
pas de effective basis of $post^*$. leur algorithme n'est plus un algo. ex reset PN ?
\end{proof}

\begin{theorem}
{\sc resilience} is undecidable for WSTS (with upward compatibility).
\end{theorem}
